Dynamic Knapsack Problem

### 2021-07-26 v2-Manuscript/Manuscript.tex
added non - carry over option

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ul}, \vec{pw}, \vec{ps}) v(\vec{ul}, \vec{pw}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 +
		\bigg( \beta^{ul}_{p} (\hat{ul}_{p} + uen_{d}) \bigg) + \\  
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ul}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\begin{equation}
	\beta^{0}: \qquad (1-\gamma) \beta^{0}
\end{equation}
\begin{equation}
\beta^{ul}_{p}: \qquad 
	\sum_{p} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big)
\end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{pw}_{mdc}: \qquad 
	&& \sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) + 
	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
	\Big( pw_{mdc} - \gamma 
		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
&	&& \sum_{dc} \beta_{Mdc}^{pw} 
	\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
\end{alignedat} \end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{ps}_{tmdc}: \qquad 
	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
&	&& 
	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
	\Big( ps_{tmdc} - \gamma 
		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
\end{alignedat} \end{equation}

@@

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ul}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}]
		&&	\forall p \\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
		&&	\forall dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
		&&	\forall m \in \{1...M-1\} dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
		&&	\forall dc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
		&&	\forall tdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
		&&	\forall mdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
		&&	\forall \{1...T-1\} dc
\end{alignat}

>>>>

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ul}, \vec{pw}, \vec{ps}) v(\vec{ul}, \vec{pw}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 +
		\bigg( \beta^{ul}_{p \in \text{co}} (\hat{ul}_{p} + uen_{d}) \bigg) + 
		\bigg( \beta^{ul}_{p \in \text{nco}} (uen_{d}) \bigg) + \\  
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ul}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\begin{equation}
	\beta^{0}: \qquad (1-\gamma) \beta^{0}
\end{equation}
\begin{equation}
\beta^{ul}_{p}: \qquad 
	\sum_{p \in \text{co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
	\sum_{p \in \text{nco}} \beta_{p}^{ul} ( ul_{p}) 
\end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{pw}_{mdc}: \qquad 
	&& \sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) + 
	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
	\Big( pw_{mdc} - \gamma 
		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
&	&& \sum_{dc} \beta_{Mdc}^{pw} 
	\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
\end{alignedat} \end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{ps}_{tmdc}: \qquad 
	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
&	&& 
	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
	\Big( ps_{tmdc} - \gamma 
		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
\end{alignedat} \end{equation}

@@

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ul}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
		&&	\forall p \in \{ \text{carry over} \} \\ 
	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
		&&	\forall p \in \{ \text{non carry over} \}\\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
		&&	\forall dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
		&&	\forall m \in \{1...M-1\} dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
		&&	\forall dc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
		&&	\forall tdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
		&&	\forall mdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
		&&	\forall \{1...T-1\} dc
\end{alignat}
